Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-22 Manuscript/sec4-experiments.tex
update GaAN

\paragraph{GaAN}
The top basic operator was \texttt{addmm}. 
The \texttt{addmm}, the matrix multiplication \texttt{mm} and the elementwise multiplication \texttt{mul} were used in both the vertex and the edge calculation, where the edge calculation is dominant.

>>>>

\paragraph{GaAN}
The top basic operator was \texttt{bmm} used in the message function $\phi$. 
The \texttt{addmm} operator and the \texttt{mm} operator were used in both the vertex and the edge calculation, where the edge calculation is dominant.
